\pdfoutput=1
%The other issue is that some packages, such as microtype, produce different output under pdflatex. By default the arXiv goes from dvi to ps to pdf, so if you need pdflatex you have to set the \pdfoutput flag in the TeX file.
\newif\ifpersonal
\newif\ifarxiv
\personaltrue % comment to remove personal notes
\arxivtrue % comment to display shortened version for journal submissions
\RequirePackage[l2tabu, orthodox]{nag} %detect whether obsolete packages are used
\documentclass[10pt,a4paper,reqno,oneside]{book} %reqno places equation numbers on the right
\linespread{1.2}
%\allowdisplaybreaks[1]
\usepackage{calligra}
\usepackage{amsmath,amsthm,amssymb,mathrsfs,mathtools,bm,eucal,tensor} % math related
\usepackage{microtype,fixltx2e} % latex technical issues
\usepackage[scaled]{beramono,berasans}
\usepackage{enumerate,comment,braket,xspace,tikz-cd} %utilities
\usepackage[all,cmtip]{xy} % utilities
\usepackage[utf8]{inputenc} % input encoding
\usepackage[T1]{fontenc} % font encoding
\usepackage{lmodern}
\definecolor{linkcolor}{HTML}{005050}
\usepackage[centering,vscale=0.7,hscale=0.7]{geometry}
\usepackage{hyperref}
\usepackage[capitalize]{cleveref}
\usepackage{graphicx}
\usepackage{xparse}
\usepackage{url}

%\makeevenhead{headings}{\thepage}{}{\leftmark}
%\setlrmarginsandblock{3cm}{3.5cm}{*}
%\setlength\marginparwidth{2.5cm}
%\checkandfixthelayout
%
%\setlength\headheight{24pt}

\usepackage{vmargin}
\setpapersize{A4}
\setmarginsrb{25mm}{10mm}{25mm}{10mm}%
{12mm}{10mm}{5mm}{10mm}

\usepackage{fancyhdr}
\pagestyle{fancy}
%%%Settings
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\renewcommand{\sectionmark}[1]{\markright{\thesection\ #1}}
\fancyhf{}
\fancyhead[LE,RO]{\bfseries\thepage}
\fancyhead[RE]{\bfseries\footnotesize\nouppercase{\leftmark}}
\fancyhead[LO]{\bfseries\footnotesize\nouppercase{\rightmark}}

\theoremstyle{plain}
\newtheorem{thm-intro}{Theorem}
\newtheorem{thm}{Theorem}[section]
\newtheorem*{thm*}{Theorem}
\newtheorem{lem}[thm]{Lemma}
\newtheorem*{lem*}{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{conj}[thm]{Conjecture}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{cor-intro}[thm-intro]{Corollary}
\newtheorem{assumption}[thm]{Assumption}
\theoremstyle{definition}
\newtheorem{defin}[thm]{Definition}
\newtheorem{question}[thm]{Question}
\newtheorem{exercise}[thm]{Exercise}
\newtheorem{defin-intro}[thm-intro]{Definition}
\newtheorem{notation}[thm]{Notation}
\theoremstyle{remark}
\newtheorem*{rem*}{Remark}
\newtheorem{eg}[thm]{Example}
\newtheorem{eg-intro}[thm-intro]{Example}
\newtheorem{rem}[thm]{Remark}
\newtheorem{rem-intro}[thm-intro]{Remark}
\numberwithin{equation}{section}
\newtheorem{construction}[thm]{Construction}

\input{newcommands_all}

\title{Derived Algebraic Geometry Seminar: UPenn 2017}

\begin{document}

\maketitle
\tableofcontents

\chapter*{Introduction}
\addcontentsline{toc}{chapter}{Introduction} \markboth{INTRODUCTION}{}

This contains notes for the Derived Algebraic Geometry Seminar currently being held at the University of Pennsylvania 
math department in the 2016-17 academic year. Having introduced the machinery of Derived Algebraic Geometry the previous semester,
we investigate its applications to producing Virtual Fundamental Cycles. Initially we will focus on moduli spaces of stable
maps, with various boundary conditions, and how VFCs for these can be used to construct Gromov-Witten invariants and Floer-type
theories.

This is a draft and errors should be expected.




\input{vfc_ch1_gw}
\input{vfc_ch2_obs}
\input{vfc_ch3_geom}
\input{vfc_ch4_k3}
\input{vfc_ch5_abelian}
\input{vfc_ch6_Stable}
\input{vfc_ch7_pardon}
\input{vfc_ch8_DMan}
\input{vfc_ch9_infinity}
\input{vfc_ch10_Geometries}
\input{vfc_ch11_stacks_cobordism}


\chapter{Benedict on comparing VFCs}
Recall the definition of derived cobordism, in particular the relative version over $K(\pi, n)$. Working over a derived manifold
$X$ which admits a presentation with a single quasi-smooth chart, we know that both approaches to VFC give the Euler class of
$E^1 \to E^2$. The next case is a hypercover of the form:
\[
\begin{tikzcd}
\; & U_{12}\arrow{dr}\arrow{dl} & \\
U_1\arrow{dr} & & U_2\arrow{dl} \\
 & X & 
\end{tikzcd}
\]
Note that cohomology is $\pi_0$ of the following space:
\[	\Map (X,K(\pi,n)) \cong \lim_I \Map\big(U_I, K(\pi,n)\big) . \]
We have a class $[U_I] \in \pi_0 \Map\big(U_I,K(\pi,n)\big)$, for any $I \subset S$. We would want to lift this to
an element $[\tilde U_I] \in \Map\big(U_I,K(\pi,n)\big)$. We would glue these to get $[X] \in \Map\big(X,K(\pi,n)\big)$.

\begin{conj}
Pick any consistent set of representatives $[\tilde U_i]$ that agree on the maps in the colimit system. Then
$\pi_0([\tilde X]) \in \pi_0 \Map\big(X,K(\pi,n)\big)$ is independent of the lifts.
\end{conj}

In other words, we have a topological space ConsLift. We claim that this is contractible and non-empty.



The big picture should be as follows. We know that for any topological space $X$ we have an isomorphism 
$\pi_0 \Map (X,K(\Z,n)) \to H^n(X)$. We want to see some chain level version of this, i.e. that the space
$\Map (X,K(\pi,n))$ determines the dg vector space $C^{\bullet}(X)$. For this, let $\Omega^{\bullet}K$ denote the
Eilenberg-Maclane spectrum for $\Z$. Write $X = \colim \Delta_i$, where the colimit is indexed over all simplices mapping to $X$
(i.e. we will be using the singular model for cochains). Then we have the diagram:
\[
\begin{tikzcd}
\Map (X, \Omega^{\bullet}K) \arrow{r}{\simeq} & \lim \Map(\Delta_i, \Omega^{\bullet} K) \arrow{d} \\
C^{\bullet}(X) \arrow{r}{\simeq} & \lim H^0(\Delta_i)[-\dim \Delta_i] .
\end{tikzcd}
\]
The upper horizontal map is an iso because mapping spaces preserve colimits under appropriate assumptions. \todo{work out}
The lower horizontal map is an iso by definition of singular homology. The vertical map is obtained by factoring through
$\Map(\Delta_i, K(\Z, 0))$ and then passing to $\pi_0$ of this space which is $\Z$.

Now, given the VFC constructed via cobordism in Spivak, it is an element $[X] \in \pi_0 \Map (X,\Omega K)$.
\begin{enumerate}
\item Choose a lifting $[\tilde X] \in \Map(X,\Omega K)$.
\item Given an atlas $[U_I]$, this gives elements $[\tilde U_I] \in \Map(U_I,\Omega K)$.
\item Using the diagram we just constructed, this gives $[\tilde U_I] \in C^{\bullet}(U_I)$.
\item Using some appropriate chain level quasi-isomorphism \todo{work out}, this gives $[\tilde U_I] \in C^{\bullet}_{\vir}(U_I)$.
\item Using Pardon's gluing construction, we obtain $[X^P] \in C_{\vir}^{\bullet}(X)$.
\item We want to compare $[\tilde X]$ with $[X^P]$. They won't agree at chain level, because we made an arbitrary choice
of lifting $[\tilde X]$ for $[X]$. \todo{can we make a non-arbitrary choice?} But the cohomology classes they define should agree.
\end{enumerate}

\todo{This outline looks good, but we've been assuming $[X]$ is a cohomology class, when in fact it's a homology class.
We need to change things appropriately. In particular, the relationship of $[X]$ with the mapping space
$\Map(X, \Omega^{\bullet}K)$ is more complicated than $[X] \in \pi_0 \Map(X, \Omega^{\bullet}K)$.}



\bibliographystyle{plain}
\bibliography{dahema}

\end{document}




